---
title: "pfDesign: An Adaptive Platform Trial Design Toolbox"
author: "Chenguang Wang"
date: "`r Sys.Date()`"
output:
    pdf_document:
      keep_tex:  true
    ## rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pfDesign: An Adaptive Platform Trial Design Toolbox}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Introduction

In the *R* package **pfDesign**, we implement functions for the design and
analysis of adaptive platform trials. The package is currently available on
GitHub, and can be installed in *R* as follows:

```{r, eval=F, echo=TRUE}
require(devtools)
install_github("olssol/pfDesign")
```

After installation, the package can be loaded in *R* as follows:

```{r, eval=T, echo=TRUE}
require(pfDesign)
```

# Major Function

The major function provided in **pfDesign** is **pdFilter**, which implements a particle filter
algorithm for posterior sampling with a TEA prior. The function is defined as follows:

```{r, eval=F, echo=TRUE}
pdFilter(vec_y, vec_interval, nsmps = 5000, epsilons = 1, ...)
```
The main parameters for **pdFilter** are

1. *vec_y*: Vector of binary outcomes
2. *vec_interval*: Vector of interval indices
3. *epsillon*: Mixture proportions $\epsilon$
4. *nsmps*: Number of posterior samples

# Example

The following is an example for applying the function *pdFilter* to obtain
posterior samples. In the example, we set $\epsilon_k \equiv 0.5$, and create
two intervals, split at day $100$.

```{r, eval=T, echo=TRUE}
## load example data in  pfDesign
data(ex_dta)

## create time intervals based on enrollment time
vec_interval <- as.numeric(cut(ex_dta$Enroll_Time,
                               breaks = c(-Inf, 100, Inf)))

## binary outcome
vec_y <- ex_dta$Outcome

## get posterior samples
post_smps <- pdFilter(vec_y,
                      vec_interval,
                      nsmps = 5000,
                      epsilons = 0.5)
```

The results are returned as a *data.frame* in *post_smps*. The following code
generates the density plots for the posterior samples after interval 1 and 2.

```{r, eval=F, echo=TRUE}
post_smps$interval <- as.factor(post_smps$interval)
ggplot(data = post_smps, aes(x = theta, group = interval)) +
    stat_density(aes(color = interval),
                 position = "identity",
                 geom = "line", adjust = 1) +
    theme_bw()
```{r, eval=T, echo=TRUE}
